---
title: "LinearModel"
author: "Kayleen Hernandez"
date: "10/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
require(tidyverse)
require(tigerstats)
```

# Introduction

Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova.

## SIMS~ARM Regression 

```{r}
plot(SIMS~ARM,data=data)
```




```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```

  
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
```{r}
basicNN + geom_point() + geom_smooth(method=lm)
```




The greater the pounds of force(ARM), the greater the simulation(SIMS)

This scatter plot shows the blue line which is an indication of a best linear fit to predict what an avergage sim response would be for any ARM strength. 

the shaded part is the uncertainty of the blue line itself.

```{r}
cor(SIMS~ARM,data=data)
```

This number is the correlation between SIMS and ARM force. Correlation is a measure of the linear association between the two variables. 

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The equation is SIMS = -4.095160 + 0.054563 * ARM 


```{r}
newData=data.frame(GRIP=94,ARM=88)
predict.lm(model.1,newData,interval="prediction")
```

Fit is the predicted ARM score when you have anARM strenght of 88. 

The LWR and UPR are the 95% confidence intervals for predicted SIMS score ARM is 88. 

## SIMS~GRIP Regression

```{r}
plot(SIMS~GRIP,data=data)
```


## SIMS~ARM+GRIP Rgression

## MODEL COMPARISONS