---
title: "LinearModel"
author: "Kayleen Hernandez"
date: "10/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
require(tidyverse)
require(tigerstats)
```

# Introduction

Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova.

## SIMS~ARM Regression 

```{r}
plot(SIMS~ARM,data=data)
```
ggplot

The greater the pounds of force(ARM), the greater the simulation(SIMS)


```{r}
cor(SIMS~ARM,data=data)
```

This number is the correlation between SIMS and ARM force. Correlation is a measure of the linear association between the two variables. 

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The equation is SIMS = -4.095160 + 0.054563 * ARM 


## SIMS~GRIP Regression


## SIMS~ARM+GRIP Rgression

## MODEL COMPARISONS